---
title: "AI Risk Assessment Report"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  html_document:
    self_contained: true
    toc: true
    toc_float: true
    theme: flatly
    highlight: tango
params:
  report_info: NA
  summary: NA
  answers: NA
  domain_scores: NA
  recommendations: NA
  red_flags: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)

library(dplyr)
library(knitr)
library(ggplot2)
library(scales)
```

<style>
body {
  font-size: 15px;
}

h1, h2, h3 {
  color: #17365d;
}

.verdict-box {
  border-left: 8px solid #17365d;
  background-color: #f2f6fa;
  padding: 18px;
  margin: 20px 0;
  border-radius: 4px;
}

.warning-box {
  border-left: 8px solid #d9534f;
  background-color: #fdf2f2;
  padding: 18px;
  margin: 20px 0;
  border-radius: 4px;
}

.action-box {
  border-left: 8px solid #f0ad4e;
  background-color: #fff9ed;
  padding: 18px;
  margin: 20px 0;
  border-radius: 4px;
}

table {
  width: 100%;
}

th {
  background-color: #17365d;
  color: white;
}

.page-break {
  page-break-before: always;
}
</style>

# Assessment information

```{r report-information}
knitr::kable(
  params$report_info,
  col.names = c("Report information", "Value"),
  format = "html",
  escape = TRUE,
  table.attr = 'class="table table-striped table-bordered"'
)
```

# Overall assessment

<div class="verdict-box">

## `r params$summary$result[params$summary$measure == "Overall AI risk verdict"]`

This is the overall AI RiskCheck verdict after considering inherent risk, safeguards and any mandatory escalation conditions.

</div>

```{r overall-summary}
knitr::kable(
  params$summary,
  col.names = c("Measure", "Result"),
  format = "html",
  escape = TRUE,
  table.attr = 'class="table table-striped table-bordered"'
)
```



# Mandatory escalation conditions

```{r red-flags, results="asis"}
if (length(params$red_flags) == 0) {

  cat(
    "<p>No mandatory escalation conditions were identified.</p>"
  )

} else {

  cat('<div class="warning-box">')
  cat("<strong>The following escalation conditions were identified:</strong>")
  cat("<ul>")

  for (flag in params$red_flags) {
    cat(
      paste0(
        "<li>",
        htmltools::htmlEscape(flag),
        "</li>"
      )
    )
  }

  cat("</ul>")
  cat("</div>")
}
```

# Risk by assessment domain

```{r domain-chart, fig.width=9, fig.height=6}
if (nrow(params$domain_scores) > 0) {

  ggplot(
    params$domain_scores,
    aes(
      x = reorder(domain, risk_score),
      y = risk_score
    )
  ) +
    geom_col(fill = "#2c6f9e") +
    geom_text(
      aes(
        label = paste0(
          round(risk_score),
          "%"
        )
      ),
      hjust = -0.1
    ) +
    coord_flip() +
    scale_y_continuous(
      limits = c(0, 110),
      labels = function(x) {
        paste0(x, "%")
      }
    ) +
    labs(
      x = NULL,
      y = "Risk / control concern",
      title = "AI risk profile"
    ) +
    theme_minimal(
      base_size = 12
    )
}
```

```{r domain-table}
domain_table <- params$domain_scores %>%
  select(
    Domain = domain,
    `Risk / control concern` = risk_score,
    Rating = rating
  ) %>%
  mutate(
    `Risk / control concern` = paste0(
      `Risk / control concern`,
      "%"
    )
  )

knitr::kable(
  domain_table,
  format = "html",
  escape = TRUE,
  table.attr = 'class="table table-striped table-bordered"'
)
```

# Recommended assurance

```{r recommendations, results="asis"}
cat("<ul>")

for (recommendation in params$recommendations) {
  cat(
    paste0(
      "<li>",
      htmltools::htmlEscape(recommendation),
      "</li>"
    )
  )
}

cat("</ul>")
```

<div class="page-break"></div>

# Assessment answers

The tables below provide a summary of every assessment question, the selected answer, the numerical rating and the resulting level of concern.

```{r answer-summary, results="asis"}
answer_domains <- unique(
  params$answers$domain
)

for (current_domain in answer_domains) {

  cat(
    paste0(
      "<h2>",
      htmltools::htmlEscape(current_domain),
      "</h2>"
    )
  )

  domain_answers <- params$answers %>%
    filter(
      domain == current_domain
    ) %>%
    transmute(
      Question = question,
      Answer = response_label,
      Rating = response_rating,
      Concern = concern_rating,
      Weight = weight
    )

  print(
    knitr::kable(
      domain_answers,
      format = "html",
      escape = TRUE,
      row.names = FALSE,
      table.attr = 'class="table table-striped table-bordered"'
    )
  )
}
```

