---
title: "AI RiskCheck Assessment Report"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  html_document:
    self_contained: true
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    number_sections: false
    theme: flatly
    highlight: tango
params:
  app_name: "AI RiskCheck"
  app_version: NA
  classification: NA
  report_information: NA
  system_profile: NA
  results_summary: NA
  decision_summary: NA
  domain_scores: NA
  flags: NA
  key_risks: NA
  recommendations: NA
  additional_considerations: NA
  answers: NA
  references: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  results = "asis"
)

library(dplyr)
library(ggplot2)
library(knitr)
library(htmltools)
```

<style>

body {
  color: #0b0c0c;
  font-size: 15px;
  line-height: 1.55;
}

h1,
h2,
h3 {
  color: #003764;
  font-weight: 800;
}

h1 {
  border-bottom: 6px solid #347CA9;
  padding-bottom: 12px;
}

h2 {
  border-bottom: 3px solid #347CA9;
  padding-bottom: 7px;
  margin-top: 32px;
}

h3 {
  margin-top: 25px;
}

.classification-banner {
  background-color: #fff8cc;
  border: 2px solid #ffdd00;
  padding: 10px 15px;
  margin-bottom: 25px;
  text-align: center;
  font-weight: 800;
}

.verdict-box {
  background-color: #f4f8fb;
  border-left: 8px solid #1d70b8;
  padding: 20px;
  margin: 20px 0;
}

.action-box {
  background-color: #fff8cc;
  border-left: 8px solid #ffdd00;
  padding: 18px;
  margin: 20px 0;
}

.stop-box {
  background-color: #fcf5f5;
  border-left: 8px solid #ca3535;
  padding: 18px;
  margin: 20px 0;
}

.escalate-box {
  background-color: #fff8cc;
  border-left: 8px solid #f47738;
  padding: 18px;
  margin: 20px 0;
}

.success-box {
  background-color: #f3f8f6;
  border-left: 8px solid #0f7a52;
  padding: 18px;
  margin: 20px 0;
}

.incomplete-box {
  background-color: #f4f4f4;
  border-left: 8px solid #6f777b;
  padding: 18px;
  margin: 20px 0;
}

table {
  width: 100%;
  margin-bottom: 25px;
}

table th {
  background-color: #003764 !important;
  color: white !important;
  font-weight: 800;
}

table td,
table th {
  padding: 9px !important;
  vertical-align: top !important;
}

table tbody tr:nth-child(odd) {
  background-color: #f4f8fb;
}

.question-block {
  border: 1px solid #cecece;
  border-left: 6px solid #347CA9;
  padding: 16px;
  margin: 16px 0 24px 0;
  page-break-inside: avoid;
}

.question-number {
  display: inline-block;
  background-color: #003764;
  color: white;
  width: 29px;
  height: 29px;
  line-height: 29px;
  text-align: center;
  border-radius: 50%;
  font-weight: 800;
  margin-right: 8px;
}

.answer-label {
  color: #003764;
  font-weight: 800;
}

.report-footer {
  border-top: 3px solid #347CA9;
  margin-top: 40px;
  padding-top: 15px;
  color: #484949;
  font-size: 13px;
}

.page-break {
  page-break-before: always;
}

@media print {

  .tocify {
    display: none;
  }

  body {
    font-size: 12px;
  }

  a {
    color: #0b0c0c;
    text-decoration: none;
  }
}

</style>

<div class="classification-banner">

`r params$classification`

</div>

# `r params$app_name` Assessment Report

This report records the AI system profile, assessment responses, notes, scores, escalation conditions and recommended assurance activities captured through AI RiskCheck.

# Report information

```{r report-information}
print(
  knitr::kable(
    params$report_information,
    col.names = c(
      "Report information",
      "Value"
    ),
    format = "html",
    escape = TRUE,
    row.names = FALSE,
    table.attr = 'class="table table-striped table-bordered"'
  )
)
```

# AI system profile

```{r system-profile}
print(
  knitr::kable(
    params$system_profile,
    col.names = c(
      "Profile field",
      "Information provided"
    ),
    format = "html",
    escape = TRUE,
    row.names = FALSE,
    table.attr = 'class="table table-striped table-bordered"'
  )
)
```

# Overall assessment

<div class="verdict-box">

## Overall rating: `r params$results_summary$result[params$results_summary$measure == "Overall rating"]`

</div>

```{r results-summary}
print(
  knitr::kable(
    params$results_summary,
    col.names = c(
      "Measure",
      "Result"
    ),
    format = "html",
    escape = TRUE,
    row.names = FALSE,
    table.attr = 'class="table table-striped table-bordered"'
  )
)
```

## Decision summary

<div class="action-box">

`r params$decision_summary`

</div>

# Escalation and stop conditions

```{r escalation-flags}
flag_data <- params$flags

for (i in seq_len(nrow(flag_data))) {

  severity <- flag_data$severity[i]
  issue <- flag_data$issue[i]

  box_class <- dplyr::case_when(
    severity == "STOP" ~ "stop-box",
    severity == "ESCALATE" ~ "escalate-box",
    severity == "None" ~ "success-box",
    TRUE ~ "incomplete-box"
  )

  cat(
    paste0(
      '<div class="',
      box_class,
      '"><strong>',
      htmltools::htmlEscape(severity),
      ":</strong> ",
      htmltools::htmlEscape(issue),
      "</div>"
    )
  )
}
```

# Risk profile by assessment area

```{r domain-risk-chart, results="markup", fig.width=9, fig.height=6}
if (nrow(params$domain_scores) > 0) {

  print(
    ggplot(
      params$domain_scores,
      aes(
        x = reorder(
          domain,
          risk_score
        ),
        y = risk_score
      )
    ) +
      geom_col(
        fill = "#347CA9"
      ) +
      geom_text(
        aes(
          label = paste0(
            round(risk_score),
            "%"
          )
        ),
        hjust = -0.1,
        fontface = "bold"
      ) +
      coord_flip() +
      scale_y_continuous(
        limits = c(0, 110),
        breaks = seq(
          0,
          100,
          20
        )
      ) +
      labs(
        x = NULL,
        y = "Risk / control concern (%)",
        title = "Risk profile by assessment area"
      ) +
      theme_minimal(
        base_size = 12
      ) +
      theme(
        plot.title = element_text(
          face = "bold"
        ),
        axis.text.y = element_text(
          face = "bold"
        )
      )
  )

} else {

  cat(
    '<div class="incomplete-box">',
    "No scored assessment responses are available.",
    "</div>"
  )
}
```

```{r domain-score-table}
if (nrow(params$domain_scores) > 0) {

  domain_table <- params$domain_scores %>%

    transmute(
      Domain = domain,
      `Risk / control concern` = paste0(
        risk_score,
        "%"
      ),
      Rating = rating
    )

  print(
    knitr::kable(
      domain_table,
      format = "html",
      escape = TRUE,
      row.names = FALSE,
      table.attr = 'class="table table-striped table-bordered"'
    )
  )
}
```

# Key areas requiring attention

```{r key-risks}
key_risks <- params$key_risks

for (i in seq_len(nrow(key_risks))) {

  cat('<div class="escalate-box">')

  cat(
    paste0(
      "<h3>",
      htmltools::htmlEscape(
        key_risks$domain[i]
      ),
      "</h3>"
    )
  )

  cat(
    paste0(
      "<p><strong>Question:</strong> ",
      htmltools::htmlEscape(
        key_risks$question[i]
      ),
      "</p>"
    )
  )

  if (key_risks$response[i] != "") {

    cat(
      paste0(
        "<p><strong>Response:</strong> ",
        htmltools::htmlEscape(
          key_risks$response[i]
        ),
        "</p>"
      )
    )
  }

  if (key_risks$notes[i] != "") {

    cat(
      paste0(
        "<p><strong>Notes:</strong> ",
        htmltools::htmlEscape(
          key_risks$notes[i]
        ),
        "</p>"
      )
    )
  }

  cat(
    paste0(
      "<p><strong>Concern:</strong> ",
      htmltools::htmlEscape(
        key_risks$concern[i]
      ),
      "</p>"
    )
  )

  cat(
    paste0(
      "<p><strong>Recommended action:</strong> ",
      htmltools::htmlEscape(
        key_risks$recommended_action[i]
      ),
      "</p>"
    )
  )

  cat("</div>")
}
```

# Recommended assurance activities

```{r recommendations}
cat("<ul>")

for (
  recommendation in
  params$recommendations
) {

  cat(
    paste0(
      "<li>",
      htmltools::htmlEscape(
        recommendation
      ),
      "</li>"
    )
  )
}

cat("</ul>")
```

# Additional considerations

<div class="action-box">

`r params$additional_considerations`

</div>

<div class="page-break"></div>

# Summary of all assessment answers

The following section records every question, the selected answer, user notes, question-level concern, relevant principle and recommended action.

```{r assessment-answer-summary}
answer_domains <- unique(
  params$answers$domain
)

for (
  current_domain in
  answer_domains
) {

  cat(
    paste0(
      "<h2>",
      htmltools::htmlEscape(
        current_domain
      ),
      "</h2>"
    )
  )

  domain_answers <- params$answers %>%

    filter(
      domain == current_domain
    )

  for (
    i in seq_len(
      nrow(domain_answers)
    )
  ) {

    current_answer <-
      domain_answers[i, ]

    cat('<div class="question-block">')

    cat(
      paste0(
        '<p><span class="question-number">',
        current_answer$question_number,
        '</span><strong>',
        htmltools::htmlEscape(
          current_answer$question
        ),
        "</strong></p>"
      )
    )

    cat(
      paste0(
        '<p><span class="answer-label">Answer:</span> ',
        htmltools::htmlEscape(
          current_answer$response_text
        ),
        "</p>"
      )
    )

    cat(
      paste0(
        '<p><span class="answer-label">Rating:</span> ',
        htmltools::htmlEscape(
          current_answer$raw_rating
        ),
        "</p>"
      )
    )

    cat(
      paste0(
        '<p><span class="answer-label">Concern:</span> ',
        htmltools::htmlEscape(
          current_answer$concern
        ),
        "</p>"
      )
    )

    cat(
      paste0(
        '<p><span class="answer-label">User notes / rationale:</span> ',
        htmltools::htmlEscape(
          current_answer$report_notes
        ),
        "</p>"
      )
    )

    cat(
      paste0(
        '<p><span class="answer-label">Relevant principle:</span> ',
        htmltools::htmlEscape(
          current_answer$principle
        ),
        "</p>"
      )
    )

    cat(
      paste0(
        '<p><span class="answer-label">Recommended action:</span> ',
        htmltools::htmlEscape(
          current_answer$recommended_action
        ),
        "</p>"
      )
    )

    cat("</div>")
  }
}
```

<div class="page-break"></div>


# Sources and supporting references

```{r reference-list}
reference_data <- params$references

for (
  i in seq_len(
    nrow(reference_data)
  )
) {

  cat(
    paste0(
      "<h3>",
      htmltools::htmlEscape(
        reference_data$source[i]
      ),
      "</h3>"
    )
  )

  cat(
    paste0(
      "<p><strong>Organisation:</strong> ",
      htmltools::htmlEscape(
        reference_data$organisation[i]
      ),
      "</p>"
    )
  )

  cat(
    paste0(
      "<p><strong>Date:</strong> ",
      htmltools::htmlEscape(
        reference_data$date[i]
      ),
      "</p>"
    )
  )

  cat(
    paste0(
      "<p>",
      htmltools::htmlEscape(
        reference_data$purpose[i]
      ),
      "</p>"
    )
  )

  cat(
    paste0(
      '<p>',
      htmltools::htmlEscape(
        reference_data$url[i]
      ),
      '',
      "Open original source",
      "</a></p>"
    )
  )
}
```

# Important limitations

AI RiskCheck is a decision-support tool. It does not replace professional judgement, analytical quality assurance, information assurance, security, data protection, legal, commercial or other required departmental approval processes.

The scoring methodology and thresholds are currently at prototype stage and require internal validation. The assessment should be reviewed whenever the model, prompt, data source, intended use, affected user group, level of autonomy, supplier, environment or lifecycle stage materially changes.

<div class="report-footer">

**Application:** `r params$app_name`  
**Version:** `r params$app_version`  
**Classification:** `r params$classification`  
**Report generated:** `r format(Sys.time(), "%d %B %Y at %H:%M")`

</div>